Dismal Code: Studying the Evolution of Security Vulnerabilities

### 2013-02-03 docs/msr.tex
more on the ecperiment section

\subsection{Data Provenance and Processing}
\label{sec:data}

>>>>

Our experiment goal was to collect the metric results of the FindBugs tool.
The process involved four entities: a number of {\it workers}, a
{\it task queue} mechanism,\footnote{\url{http://www.rabbitmq.com/}}
a {\it data repository},\footnote{\url{http://www.mongodb.org/}}
and the {\it code repository}, which in our case it was the public Maven 
repository\footnote{\url{http://mvnrepository.com}}.

\begin{table}
\centering
\caption{Experiment software and versions}
\label{tbl:soft-version}
\begin{tabular}{r r r}
\hline
 & Software Package & version\\
 \hline
worker & Custom Python Script & 2.7\\
task queue & RabbitMQ\footnote{\url{http://www.rabbitmq.com/}} & \\
data repository & MongoDB\footnote{\url{http://www.mongodb.org/}} & \\
code repository & Maven Repository & \\
\hline
\end{tabular}
\end{table}

First, we scanned the Maven repository for appropriate {\sc jar}s.
We discuss the {\sc jar} selection process in the next 
section. With this list we created a series of processing tasks
and added them to the task queue. Then we
executed 25 (Unix-based) workers that checked out tasks from the queue,
processed the data and stored the results to the data repository.

A typical processing cycle of a worker included the following steps: after
the worker spawns, it requests a task from the queue. This task contains
the {\sc jar} name, which is typically a project version that is downloaded locally.
First, specific {\sc jar} metadata are calculated and stored. Such metadata include the
last modification date of the {\sc jar}, its size and dependencies and a number that
represents the chronological order of the release. This order is derived from an {\sc xml} file that
accompanies every project in the Maven repository called {\it
maven-metadata.xml}. Then FindBugs is executed and its' results are also stored
in the data repository. When the task is completed the queue is notified and
the next task is requested.

This process was executed for all the available {\sc jar}s in the task queue.
The experiment was executed five times in order to iron out various bugs in
our scripts and validate the results.

\subsection{Data Provenance}
\label{sec:data}
